Paper_analyses

### 2021-11-10 Paper_Analyses_subj_obje_arousal.Rmd
Inferential PCA start

polyyrelation3 <- lmer(arousal_c ~ valence_c_sq+ (1|ssid) + (1|stimIAPS),
                     REML = FALSE,
                     data = subset(db_full4new_stim_screen_pupil_nopract, )

@@

# macthed test

@@

and then we can compare these clusters on ground truth arousal and valence
- decisions to make: do we average the responses per participant and cluster at a trial level - this ignores individual variability
- what do we do with teh nested nature of teh data, one participant has multiple trials, if we don't accout for this, the cluster will treat data from different participants the same way.

If create cluster on a ndividual level- then the issue is different participants will end up with different clusters and clusters for one person are not translaable.

@@

clustering3$
cluster_lmers$scr_clust2 <- lmer(log_BIO_CDA.PhasicMax ~ y_kmeans + 
                               (1 | ssid)+
                               (1|stimIAPS),
                             REML = FALSE,
                             data = clustering3)

@@

clustering2<- subset(clustering, !is.na(stimDescription))

@@

colnames(clustering2)
clust2_dataset = clustering2[c(24,2,1,7:11,18,19)]

@@

>>>>

polyyrelation3 <- lmer(arousal_c ~ valence_c_sq+ (1|ssid) + (1|stimIAPS),
                     REML = FALSE,
                     data = subset(db_full4new_stim_screen_pupil_nopract ))

@@

@@

and then we can compare these clusters on ground truth arousal and valence
- decisions to make: do we average the responses per participant and cluster at a trial level - this ignores individual variability
- what do we do with the nested nature of teh data, one participant has multiple trials, if we don't accout for this, the cluster will treat data from different participants the same way.

If we create cluster on a individual level- then the issue is different participants will end up with different clusters and clusters for one person are not translatable.

@@

View(clustering3)
cluster_lmers$scr_clust2 <- lmer(log_BIO_CDA.PhasicMax ~ y_kmeans + 
                               (1 | ssid)+
                               (1|stimIAPS),
                             REML = FALSE,
                             data = clustering3)

@@

View(clustering)
clustering2<- subset(clustering, !is.na(stimDescription))

@@

View(clustering2)
colnames(clustering2)
clust2_dataset = clustering2[c(24,2,1,7:11,18,19)]

@@

PCA and barycentric
